Reducing iptables configuration complexity using chains

### 2014-05-04 iptables/paper.tex
add section on filters
add targets section

  \subsection{Filters}
  \subsection{Targets}

>>>>

  \subsection{Filters}

    Filter on packet properties :
    \begin{itemize}
      \item protocol (tcp, udp, icmp, \ldots)
      \item destination/source port
      \item destination/source IP address
      \item in/outgoing interface (eth0, \ldots)
      \item \ldots
    \end{itemize}

    In this example, the filter matches any TCP packet with destination port 22 (SSH) originating from the 10.0.0.0/8 network :
    \begin{verbatim}
iptables -A INPUT -m tcp -p tcp --dport ssh -s 10.0.0.0/8 -j ACCEPT
    \end{verbatim}

  \subsection{Targets}

    What happens if a packet matches a rule :
    \begin{itemize}
      \item ACCEPT
      \item DROP
      \item QUEUE $\rightarrow$ userspace
      \item RETURN $\rightarrow$ leave current chain
      \item LOG
      \item jump to a custom chain
    \end{itemize}

    In this example, the packet is accepted if it matches the rule :
    \begin{verbatim}
iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT
    \end{verbatim}
